The Death of Distance: Mobile Internet and Political Trust in Africa\\ \vspace{0.75cm} \underline{Preliminary and incomplete }

### 2025-02-24 writing/wp/method and results.tex
import folders

\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{url}
\usepackage{dcolumn}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{seqsplit}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{soul}
\usepackage{float}
%\usepackage[multiple]{footmisc}
%\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{rotating}

@@

\title{Internet and Nation Building in Africa\\  \vspace{0.75cm} \underline{Preliminary and incomplete }}

@@

\maketitle

\begin{table}[H]
    \sffamily
    \caption{{Effect of distance from the capital on political trust}}
    \centering
    %\footnotesize
    \resizebox{12cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
    \\
    \toprule
    \toprule
    &  \multicolumn{4}{c}{{OLS}}  \\
    \cmidrule(r){2-5}
    &  \multicolumn{4}{c}{{Political trust}}  \\
    \cmidrule(r){2-5}
    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
        \cmidrule(r){2-3}
        \cmidrule(r){4-5}
        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
     \midrule

     Distance from the capital&       0.284***&       0.270***&       0.681***&       0.397* \\
     \medskip
     &      (0.04)   &      (0.03)   &      (0.16)   &      (0.21)  \\
     \midrule
     \smallskip
    Individual \& regional controls  & Yes & Yes & Yes & Yes  \\
    \smallskip
    Country controls & Yes& No& Yes& No\\
    \smallskip
    Round FE & Yes & No& Yes & No\\
    \smallskip
    Country X Round FE       & No & Yes& No & Yes\\
    \smallskip
    Ethnic homeland FE & No & No & Yes& Yes\\
    \smallskip
    Observations           & 98,235   &       98,235   &        4,189   &        4,189   \\
    Adjusted-R$^2$        &       0.158   &       0.197   &       0.159   &       0.189   \\

                          \bottomrule
    \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}
    }
    \end{table}

    \begin{table}[H]
        \sffamily
        \caption{Effect of internet coverage on political trust by distance}
        \centering
        %\footnotesize
        \resizebox{17cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{5}{c}{{Base sample}}\\
        \cmidrule(r){2-6}
        & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-5}
            \cmidrule(r){6-6}
            & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet coverage}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet coverage}} & \multicolumn{1}{c}{{Political trust}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){5-5}    
            \cmidrule(r){6-6}    
            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

            \midrule

    Distance from the capital &0.463***&&&& 1.361***\\      
    \smallskip
    &      (0.05)   &&&&     (0.49)   \\
    Internet coverage     &       0.029   &&&&       1.470**  \\
    \smallskip
    & (0.06)   &&&&      (0.64)    \\ 
    \smallskip
    Distance from the capital $\times$ Internet coverage&      -0.480***&&&               &       -2.295**\\
    \smallskip  &       (0.10)   &&&               &      (1.09) \\

   Lightning strikes && -0.002*** && -0.000  \\
    \smallskip&& (0.00) && (0.00) \\
    Distance from the capital city $\times$ Lightning strikes&& 0.000 && -0.001**\\
    \medskip&& (0.00) && (0.00)\\

         \midrule
        SW \emph{F} - Lightning strikes &-&-& 19.66&- &-&-\\
        \smallskip
        SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 11.13 &-&-&-\\
        \smallskip
        Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes & Yes&- & Yes & Yes \\
        \smallskip
        Observations       &       98,235    &99,414 && 99,414&       98,235  \\
        Adjusted-R$^2$    &       0.198    &-&-&-&  \\
                              \bottomrule
        \multicolumn{6}{p{27cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the region x round level. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}}
        \end{table}

        \begin{table}[H]
            \sffamily
            \caption{{Other outcomes}}
            \centering
            %\footnotesize
            \resizebox{18cm}{!}{
            \begin{tabular}{@{\extracolsep{5pt}} l c c}
            \\
            \toprule
            \toprule
            & \multicolumn{2}{c}{2SLS}\\
            \cmidrule(r){2-3}
            &\multicolumn{1}{c}{{Vote against ruling party}}&  \multicolumn{1}{c}{{Country performance}}  \\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            & \multicolumn{1}{c}{{Base sample}} & \multicolumn{1}{c}{{Base sample}}\\
                \cmidrule(r){2-2}
                \cmidrule(r){3-3}
                & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
             \midrule

             Distance from the capital&   -1.306***&       1.560***\\
             \smallskip
             &      (0.40)   &      (0.52)   \\
             Internet coverage     &      -1.370***&       1.565**  \\
             \smallskip
             &      (0.47)   &      (0.62)   \\
             Distance from the capital $\times$ Internet coverage&       2.614***&      -3.065***\\
             \medskip
             &       (0.92)   &      (1.16)   \\
             \midrule
             \smallskip
            Individual \& regional controls  & Yes & Yes\\
            \smallskip
            Country X Round FE       & Yes& Yes\\
            \smallskip
            Observations      &       99,414   &       98,512  \\            \bottomrule
            \multicolumn{3}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
            includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
            education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
            \end{tabular}
            }
            \end{table}

            \begin{table}[H]
              \sffamily
              \caption{{Media and institutions freedom}}
              \centering
              %\footnotesize
              \resizebox{16cm}{!}{
              \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
              \\
              \toprule
              \toprule
              & \multicolumn{4}{c}{2SLS: Political trust}\\
              \cmidrule(r){2-5}
              & \multicolumn{4}{c}{{Base sample}}\\
              \cmidrule(r){2-5}
              &\multicolumn{2}{c}{{Media}}&  \multicolumn{2}{c}{{Institutions}}\\
              \cmidrule(r){2-3}
                  \cmidrule(r){4-5}
                  & \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}& \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}\\
                  \cmidrule(r){2-2}
                  \cmidrule(r){3-3}
                  \cmidrule(r){4-4}
                  \cmidrule(r){5-5}
                  & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
               \midrule

               Distance from the capital&     -4.922   &       1.133*** &       0.078   &       2.151***\\
               \smallskip
               &     (11.77)   &      (0.41)  &      (0.83)   &      (0.77)\\
               Internet coverage        &      -3.475   &       1.220* &       0.112   &       2.964***\\
               \smallskip
               &     (10.01)   &      (0.68)  &      (1.37)   &      (1.06) \\
            Distance from the capital $\times$ Internet coverage&       9.210   &      -2.160* &       0.391   &      -4.202**\\
            \medskip
            &     (21.19)   &      (1.22) &      (1.59)   &      (1.90)\\

               \midrule
               \smallskip
              Individual \& regional controls  & Yes & Yes & Yes & Yes\\
              \smallskip
              Country X Round FE       & Yes& Yes & Yes& Yes\\
              \smallskip
              Observations          &       48,174   &       50,061 &       45,238   &       52,997 \\
              \bottomrule
              \multicolumn{5}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
              includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
              education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
              \end{tabular}
              }
              \end{table}

              \begin{table}[H]
                \sffamily
                \caption{{Individual heterogeneity}}
                \centering
                %\footnotesize
                \resizebox{16cm}{!}{
                \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c}
                \\
                \toprule
                \toprule
                & \multicolumn{8}{c}{2SLS: Political trust}\\
                \cmidrule(r){2-9}
                & \multicolumn{8}{c}{{Base sample}}\\
                \cmidrule(r){2-9}
                &\multicolumn{2}{c}{{Education}}&  \multicolumn{2}{c}{{Urban/Rural}}&  \multicolumn{4}{c}{{Age}}\\
                \cmidrule(r){2-3}
                    \cmidrule(r){4-5}
                    \cmidrule(r){6-9}
                    & \multicolumn{1}{c}{{$<$ Secondary}} & \multicolumn{1}{c}{{$\geq$ Secondary}}& \multicolumn{1}{c}{{Urban}} & \multicolumn{1}{c}{{Rural}} & \multicolumn{1}{c}{{18-25}}& \multicolumn{1}{c}{{26-35}}& \multicolumn{1}{c}{{36-44}}& \multicolumn{1}{c}{{45+}}\\
                    \cmidrule(r){2-2}
                    \cmidrule(r){3-3}
                    \cmidrule(r){4-4}
                    \cmidrule(r){5-5}
                    \cmidrule(r){6-6}
                    \cmidrule(r){7-7}
                    \cmidrule(r){8-8}
                    \cmidrule(r){9-9}
                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}} &  \multicolumn{1}{c}{{(6)}} &  \multicolumn{1}{c}{{(7)}} &  \multicolumn{1}{c}{{(8)}}\\
                 \midrule

                 Distance from the capital&       1.208***&       1.394   &       1.133** &       1.961***&       1.295** &       0.965   &       1.438** &       1.723*** \\
                 \smallskip
                 &      (0.31)   &      (1.17)   &      (0.52)   &      (0.70)   &      (0.57)   &      (0.63)   &      (0.56)   &      (0.59)   \\
                 Internet coverage  &       1.706*  &       1.271   &       0.397   &       3.374***&       1.439*  &       0.982   &       1.236*  &       2.540***\\
                 \smallskip
                 &      (0.92)   &      (1.32)   &      (0.63)   &      (1.18)   &      (0.74)   &      (0.76)   &      (0.72)   &      (0.87)   \\
                   Distance from the capital $\times$ Internet coverage&      -1.909** &      -2.422   &      -1.785*  &      -3.447*  &      -1.994   &      -1.477   &      -2.577** &      -3.103**  \\
                   \medskip
                   &      (0.83)   &      (2.41)   &      (0.98)   &      (1.81)   &      (1.24)   &      (1.38)   &      (1.28)   &      (1.39)   \\
                 \midrule
                 \smallskip
                Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes & Yes & Yes\\
                \smallskip
                Country X Round FE       & Yes& Yes & Yes& Yes & Yes& Yes & Yes& Yes\\
                \smallskip
                Observations         &       36,389   &       62,039   &       37,348   &       60,887   &       25,442   &       29,913   &       20,074   &       23,246   \\
                \bottomrule
                \multicolumn{9}{p{24cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
                includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. Education, rural/urban, and age controls are omitted from columns (1-2), (3-4), and (5-8), respectively.*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                \end{tabular}
                }
                \end{table}

            \begin{table}[H]
              \sffamily
              \caption{{Generalized trust}}
              \centering
              %\footnotesize
              \resizebox{16cm}{!}{
              \begin{tabular}{@{\extracolsep{5pt}} l c c}
              \\
              \toprule
              \toprule
              & \multicolumn{2}{c}{2SLS}\\
              \cmidrule(r){2-3}
              & \multicolumn{2}{c}{{Base sample: rounds 5 $\&$ 8}}\\
              \cmidrule(r){2-3}
                  & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Generalized trust}}\\
                  \cmidrule(r){2-2}
                  \cmidrule(r){3-3}
                  & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
               \midrule
               Distance from the capital&       1.358** &      -0.157   \\
               \smallskip
               &      (0.62)   &      (0.17)    \\
               Internet coverage    &       1.508   &      -0.101    \\
               \smallskip
               &      (0.94)   &      (0.23)   \\
               Distance from the capital $\times$ Internet coverage&      -2.161*  &       0.542   \\
               \medskip
               &      (1.22)   &      (0.33)   \\

               \midrule
               \smallskip
              Individual \& regional controls  & Yes & Yes\\
              \smallskip
              Country X Round FE       & Yes& Yes\\
              \smallskip
              Observations         &     49,404   &       49,362\\
              \bottomrule
              \multicolumn{3}{p{14cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
              includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
              education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
              \end{tabular}
              }
              \end{table}

              \begin{table}[H]
                \sffamily
                \caption{{Effect of distance from the capital on institutional trust (President, Parliament, Electoral commission)}}
                \centering
                %\footnotesize
                \resizebox{16cm}{!}{
                \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
                \\
                \toprule
                \toprule
                &  \multicolumn{6}{c}{{Trust in institutions (President, Parliament, Electoral commission)}}  \\
                \cmidrule(r){2-7}
                &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
                \cmidrule(r){2-6}
                \cmidrule(r){7-7}
                & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
                    \cmidrule(r){2-3}
                    \cmidrule(r){4-5}
                    \cmidrule(r){6-6}
                    \cmidrule(r){7-7}
                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
                 \midrule

                 Distance from the capital&    0.295***&       0.301***&       0.563***&       0.306 &       0.483***&       1.738***\\
                 \smallskip
                 &      (0.04)   &      (0.03)   &      (0.16)   &      (0.20) &      (0.05)   &      (0.58) \\
                 Internet coverage &&&&&       0.016   &       2.035*** \\
                 \smallskip

                 &&&&&      (0.06)   &      (0.71)\\
                 Distance from the capital $\times$ Internet coverage &&&&&      -0.458***&-2.992**\\
                 \medskip
                 &&&&&      (0.10) & (1.32)\\
                 \midrule
                 \smallskip
                Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
                \smallskip
                Country controls & Yes& No& Yes& No& No& No\\
                \smallskip
                Round FE & Yes & No& Yes & No& No& No\\
                \smallskip
                Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
                \smallskip
                Ethnic homeland FE & No & No & Yes& Yes& No& No\\
                \smallskip
                Observations           &   98,499   &       98,499   &        4,202   &        4,202   & 98,499   &       98,499 \\
                Adjusted-R$^2$        &        0.164   &       0.198   &       0.148   &       0.184  & 0.200   &       - \\

                                      \bottomrule
                \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
                includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                \end{tabular}
                }
                \end{table}

                \begin{table}[H]
                  \sffamily
                  \caption{{Effect of distance from the capital on trust in president}}
                  \centering
                  %\footnotesize
                  \resizebox{16cm}{!}{
                  \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
                  \\
                  \toprule
                  \toprule
                  &  \multicolumn{6}{c}{{Trust in president}}  \\
                  \cmidrule(r){2-7}
                  &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
                  \cmidrule(r){2-6}
                  \cmidrule(r){7-7}
                  & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
                      \cmidrule(r){2-3}
                      \cmidrule(r){4-5}
                      \cmidrule(r){6-6}
                      \cmidrule(r){7-7}
                      & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
                   \midrule

                   Distance from the capital&       0.287***&       0.262***&       0.799***&       0.343   &       0.473***&       1.517**\\
                   \smallskip
                   &      (0.05)   &      (0.03)   &      (0.19)   &      (0.25)   &      (0.06)   &      (0.63) \\
                   Internet coverage &&&&       &       0.047   &       1.659**  \\
                   \smallskip
                   &&&&    &      (0.07)   &      (0.81) \\
                   Distance from the capital $\times$ Internet coverage &&&&&      -0.521***&-2.654*\\
                   \medskip
                   &&&&&      (0.12)  & (1.41) \\
                   \midrule
                   \smallskip
                  Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
                  \smallskip
                  Country controls & Yes& No& Yes& No& No& No\\
                  \smallskip
                  Round FE & Yes & No& Yes & No& No& No\\
                  \smallskip
                  Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
                  \smallskip
                  Ethnic homeland FE & No & No & Yes& Yes& No& No\\
                  \smallskip
                  Observations            &       97,261   &       97,261   &        4,149   &        4,149   &       97,261   &       97,261  \\
                  Adjusted-R$^2$        &       0.137   &       0.180   &       0.180   &       0.215   &       0.182    &       - \\

                                        \bottomrule
                  \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
                  includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                  education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                  \end{tabular}
                  }
                  \end{table}

                  \begin{table}[H]
                    \sffamily
                    \caption{{Effect of distance from the capital on trust in parliament}}
                    \centering
                    %\footnotesize
                    \resizebox{16cm}{!}{
                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
                    \\
                    \toprule
                    \toprule
                    &  \multicolumn{6}{c}{{Trust in parliament}}  \\
                    \cmidrule(r){2-7}
                    &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
                    \cmidrule(r){2-6}
                    \cmidrule(r){7-7}
                    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
                        \cmidrule(r){2-3}
                        \cmidrule(r){4-5}
                        \cmidrule(r){6-6}
                        \cmidrule(r){7-7}
                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
                     \midrule

                     Distance from the capital&       0.282***&       0.279***&       0.560***&       0.471** &       0.453***&       1.124***\\
                     \smallskip
                     &      (0.04)   &      (0.03)   &      (0.17)   &      (0.21)   &      (0.05)   &      (0.39) \\
                     Internet coverage &&&&       &        0.007   &       1.169**  \\
                     \smallskip
                     &&&&    &      (0.06)   &      (0.52)   \\
                     Distance from the capital $\times$ Internet coverage &&&&&      -0.442***& -1.776**\\
                     \medskip
                     &&&&&     (0.10)   &  (0.89) \\
                     \midrule
                     \smallskip
                    Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
                    \smallskip
                    Country controls & Yes& No& Yes& No& No& No\\
                    \smallskip
                    Round FE & Yes & No& Yes & No& No& No\\
                    \smallskip
                    Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
                    \smallskip
                    Ethnic homeland FE & No & No & Yes& Yes& No& No\\
                    \smallskip
                    Observations            &      96,182   &       96,182   &        4,111   &        4,111   &       96,182   &       96,182  \\
                    Adjusted-R$^2$        &        0.130   &       0.160   &       0.102   &       0.127   &       0.161   &       - \\

                                          \bottomrule
                    \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
                    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                    \end{tabular}
                    }
                    \end{table}

                  \begin{table}[H]
                    \sffamily
                    \caption{{Effect of distance from the capital on trust in electoral commission}}
                    \centering
                    %\footnotesize
                    \resizebox{16cm}{!}{
                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
                    \\
                    \toprule
                    \toprule
                    &  \multicolumn{6}{c}{{Trust in electoral commission}}  \\
                    \cmidrule(r){2-7}
                    &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
                    \cmidrule(r){2-6}
                    \cmidrule(r){7-7}
                    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
                        \cmidrule(r){2-3}
                        \cmidrule(r){4-5}
                        \cmidrule(r){6-6}
                        \cmidrule(r){7-7}
                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
                     \midrule

                     Distance from the capital&       0.319***&       0.365***&       0.366*  &       0.206   &       0.529***&       2.588***\\
                     \smallskip
                     &     (0.04)   &      (0.03)   &      (0.19)   &      (0.23)   &      (0.06)   &      (0.84) \\
                     Internet coverage &&&&       &        0.003   &       3.252***  \\
                     \smallskip
                     &&&&    &      (0.07)   &      (0.95)   \\
                     Distance from the capital $\times$ Internet coverage &&&&&     -0.418***&  -4.606**\\
                     \medskip
                     &&&&&      (0.11)    &  (1.93) \\
                     \midrule
                     \smallskip
                    Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
                    \smallskip
                    Country controls & Yes& No& Yes& No& No& No\\
                    \smallskip
                    Round FE & Yes & No& Yes & No& No& No\\
                    \smallskip
                    Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
                    \smallskip
                    Ethnic homeland FE & No & No & Yes& Yes& No& No\\
                    \smallskip
                    Observations            &      94,926   &       94,926   &        4,035   &        4,035   &       94,926   &       94,926   \\
                    Adjusted-R$^2$        &         0.118   &       0.144   &       0.094   &       0.137   &       0.145   &       - \\

                                          \bottomrule
                    \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
                    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                    \end{tabular}
                    }
                    \end{table}

>>>>

\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{url}
\usepackage{dcolumn}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{seqsplit}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{soul}
\usepackage{float}
%\usepackage[multiple]{footmisc}
%\usepackage{longtable}

@@

\title{The Death of Distance: Mobile Internet
and Political Trust in Africa\\  \vspace{0.75cm} \underline{Preliminary and incomplete }}

@@

\maketitle
\section*{Data}
Figure 1 displays our sample of 20 Sub-Saharan African countries (in green) and their capital cities (in red). Our analysis combines Afrobarometer survey rounds 5-8 (2011-2021), providing geocoded data on public opinion, information access, and demographic characteristics for 98,235 individual respondents across these countries.\footnote{Our sample includes: Benin, Burkina Faso, Botswana, Cameroon, Ivory Coast, 
Ghana, Guinea, Kenya, Liberia, Mali, Malawi, Mozambique, Namibia, Niger, Nigeria, Sierra Leone, Tanzania, Uganda, Zambia, Zimbabwe. We exclude islands, countries with multiple capitals, and Northern African countries. We also exclude countries with missing data on mobile internet coverage and those not present in all survey rounds.}\footnote{All Afrobarometer surveys were conducted via-in-person, face-to-face interviews. The method did not change to computer-assisted interviews, thereby avoiding potential bias toward areas with mobile internet coverage.}

To measure political trust and accountability, we focus on three sets of variables from the Afrobarometer surveys. First, we construct our main dependent variable \textit{Political Trust} by averaging responses to trust questions about the president and parliament/national assembly, each measured on a 0-3 scale ('Not at all' to 'A lot').\footnote{The specific questions ask: \textit{``How much do you trust each of the following: the president, the parliament/national assembly?''}} Second, we measure electoral accountability through a binary variable indicating willingness to vote against the ruling party in hypothetical next-day elections.\footnote{Based on responses to: \textit{``If [presidential elections] were held tomorrow, which [party's candidate] would you vote for?''}} Third, we capture economic performance assessment through a 1-5 scale rating of economic conditions compared to twelve months prior.\footnote{Based on responses to: \textit{``Looking back, how do you rate economic conditions in this country compared to twelve months ago?''}}

To measure remoteness, we calculate each respondent's distance from their national capital using Afrobarometer's geocoded enumeration areas. Following Michalopoulos and Papaioannou (2014), we standardize distances by dividing each respondent's distance from the capital by the maximum distance within their country. This relative distance measure ranges from 0 (at capital) to 1 (furthest point), enabling meaningful cross-country comparisons.

We combine our Afrobarometer data with GSMA's digital maps of mobile internet coverage, providing 1x1-kilometer grid cell resolution data from mobile network providers. For regional coverage measurement, following Guriev et al. (2021) we overlay mobile coverage maps with population density data and calculate weighted averages of internet availability by region and year, using normalized population density weights. This approach ensures comparable coverage measures across regions of different sizes and population distributions.\\
The second part of our empirical strategy addresses how mobile internet expansion affects spatial disparities in political trust. To address potential omitted variable bias - arising from non-random internet infrastructure placement and the correlation between economic development and internet access - we instrument internet coverage using regional lightning strike patterns, following recent literature (Manacorda and Tesei, 2020; Guriev et al., 2021; Cariolle and Carolle, 2024). This identification strategy exploits the fact that areas with frequent lightning strikes face higher infrastructure deployment and maintenance costs, while these weather patterns are plausibly exogenous to political trust. Following Guriev et al. (2021) and Cariolle and Carolle (2024), we construct our instrument by calculating the average daily lightning strikes at the regional level using VHRFC data over 1998-2013, weighted by regional population density in 2011. This weighting accounts for two offsetting forces: while lightning strikes increase infrastructure costs, population density reduces per-capita costs by spreading infrastructure investments across more users in high-risk areas. This instrument provides plausibly exogenous variation in internet access across varying distance from the capital city.
